Data-driven Controller Design for a Fast-Pulsed Power Converter Control Application

### 2017-02-11 IPAC Abstract/Abstract.tex
testing

%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
\documentclass[journal]{IEEEtran}
%\IEEEoverridecommandlockouts  
%\overrideIEEEmargins     
\bibliographystyle{IEEEtran}
\pdfminorversion=4

\usepackage{cite}
%\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage{times}
\usepackage{xfrac}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{mathabx}
%\usepackage[thref]{ntheorem}
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{color}
%\usepackage{import}
\usepackage{graphicx,psfrag}
\usepackage{float}
\usepackage[cmex10]{amsmath}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{remark}{Remark}
\newcommand{\jo}{(e^{-j\omega})}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}
%\renewcommand{\IEEEQED}{\IEEEQEDopen}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
%\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
  %\raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize\ensuremath{#1}}}}

\title{\LARGE \bf A Robust Data-driven Controller Design Methodology for Particle Accelerator Power Converters}

%\iffalse
\author{Achille Nicoletti, Michele Martino and Alireza Karimi% <-this % stops a space

\thanks{Achille Nicoletti is with the Technology Department at
European Organization for Nuclear Research (CERN) and the Automatic Control Laboratory at
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small achille.nicoletti@cern.ch)}%
\thanks{Michele Martino is with the Technology Department at
European Organization for Nuclear Research (CERN) (email: \tt\small michele.martino@cern.ch)}%
\thanks{Alireza Karimi is with the Automatic Control Laboratory at
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small alireza.karimi@epfl.ch)}%
}
%\fi

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
A new data-driven approach using the frequency response function (FRF) of a system is proposed for designing robust $H_{\infty}$ digital controllers for particle accelerators' power converters. This design method ensures that the dynamics of a system are captured and avoids the problem of unmodeled dynamics associated with parametric models. The $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a two-degree of freedom RST controller. This controller is robust with respect to the frequency-dependent uncertainties of the frequency response function. Moreover, constraints will be imposed in order to simultaneously ensure the desired stability margins and the controller stability. A convex optimization algorithm is then implemented to obtain the controller parameters. The effectiveness of the method is illustrated by designing the controller for the Q-STRIP magnet power converter of the PS Booster accelerator upgrade project at CERN. Experimental validation in the time domain is also presented. 
\end{abstract}

\begin{IEEEkeywords}
Convex optimization, data-driven control, H-infinity, power converter control, robust control, RST %uncertainty, Smith predictor, MIMO time delay. 
\end{IEEEkeywords}

\section{Introduction}
\IEEEPARstart{M}{any} of today's  complex systems possess a multitude of uncertainties, and obtaining an accurate parametric model for such systems can be both laborious and impractical for controller synthesis. In industrial schemes, the dynamics of plants are typically approximated by low-order models, since the controller synthesis is easier to implement for lower order processes. However, this approximation can impede the  performance of a controller, since low-order models are subject to model uncertainty. A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. With the data-driven control scheme, the parametric uncertainties and the unmodeled dynamics are irrelevant and the only source of uncertainty is the measurement noise.

Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data. Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.  The widely used PID controller is usually tuned based on a set of time-domain or frequency-domain data.

Data-driven control methods using frequency-domain data are design schemes that continue to spark the interest of many researchers. The frequency-domain approach offers many advantages compared to time-domain methods :
\begin{itemize}
\item Without knowledge of the transfer function, the dynamics of a system can be captured experimentally through the frequency response.
\item Relative and absolute stability of a closed-loop system can be determined with the knowledge of the open-loop frequency response.
\item Noise disturbance generated in the system can be easily determined using frequency analysis.
\item System uncertainties can be modeled at discrete frequency points (which reduces the conservatism associated with uncertainty modeling). 
\end{itemize}
The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique. A robust frequency-domain control design method has been established in \cite{KNND13b}; this method, however, requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}. In this method, a convex optimization problem can be formulated if a linearly parameterized controller is considered; however, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity functions. In \cite{DWS09} a frequency-response method is proposed based on the $Q$-parametrization to guarantee the $\mathcal{H}_{\infty}$ performance for fixed-structure controllers. In \cite{KG10}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion. In order to obtain convexity, however, the controller is chosen to be linearly parameterized, i.e. the denominator of the controller are fixed. This limits the number of degrees of freedom of the controller, and thus impedes the controller performance. A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. The method in \cite{KG10} is extended to data-driven gain-scheduled controller design in \cite{KE13a} and multivariable decoupling controller design in \cite{GKL10b}. A public domain toolbox for Matlab is also available \cite{Kar13}. A similar approach is proposed in  \cite{HAB13}, where a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraints based on an initial stabilizing controller is used. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure. The design of controllers that are not linear in parameters (e.g. represented by rational transfer functions) using frequency domain data are studied in \cite{KNZ16}. The necessary and sufficient conditions for the existence of such controllers are developed. This method needs no initial stabilizing controller and converges to the optimal  $\mathcal{H}_{\infty}$ performance when the order of the controller goes to infinity.

%\iffalse
%Generally, it is desired to formulate a convex optimization problem for controller synthesis, since convex problems are computationally tractable. A frequency domain approach in designing the $RST$ controllers has been discussed in \cite{MRS11}, where a convex optimization problem is formulated by bounding a specific sensitivity function and specifying a desired characteristic polynomial. Robust stability, however, is not trivially achieved, since the characteristic polynomial incorporates an observer polynomial which usually needs to be tuned iteratively. With $\mathcal{H}_{\infty}$ control techniques, it is possible to eliminate the necessity of using observer polynomials for achieving proper robustness margins. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. In \cite{GKL11}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion. With this method, suitable robustness margins are attainable; however, in order to preserve convexity, this method requires one of the controller terms ($R$) to be fixed a priori\footnote{Note that the variable names for $R$ and $S$ are interchanged in \cite{GKL11}}. This limits the number of degrees of freedom of the controller, and thus impedes the controller performance.

The $RST$ controller structure is an effective discrete-time two-degree of freedom (2DOF) polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}. 
The $RST$ controller design methodology is usually based on the pole placement technique and uses the dynamic model of the physical system. In \cite{GKL11}, the data-driven frequency-domain approach of \cite{KG10} is extended to $RST$ controller design. However, in order to preserve convexity, this method requires one of the controller terms to be fixed a priori. This problem is fixed in \cite{NEK15}, where an $RST$ controller is designed in the $\mathcal{H}_{\infty}$ framework by formulating a convex optimization problem in a data-driven setting. The necessary and sufficient conditions for the existence of $RST$ controllers that satisfy the  $\mathcal{H}_{\infty}$ constraint only on one sensitivity function are also developed.

The proposed method in this paper is an extension of \cite{NEK15}, where the necessary and sufficient conditions that ensures the $\mathcal{H}_{\infty}$ performance for multiple weighted sensitivity functions is presented. Moreover, the frequency-dependent uncertainties originated from the measurement noise are taken into consideration for robust performance specifications. Additionally, since the parameters of the controller's denominator are the optimization variables, this method can lead to unstable controllers. Therefore, a sufficient condition is presented to ensure that the controller remains stable. The proposed method is then used to design a robust $RST$ controller for power converters in particle accelerators at CERN. The designed controller is implemented in the power converters to control their output current with extremely high precision. The main advantage of the proposed method for this application is to guarantee the robustness margins, high bandwidth and small tracking error by a data-driven convex optimization based approach that does not require the manual tuning of the classical pole-placement model-based approach.

The paper is organized as follows.
The class of models, controllers and control objectives are defined in section (\ref{sec:2}). Section (\ref{sec:3}) discusses the control design methodology and stability conditions of the proposed method for the $RST$ controller structure. Convex conditions are formulated based on the $\mathcal{H}_{\infty}$ criterion. Section (\ref{sec:4}) discusses the framework of the power converter control system and its functionality at CERN. Section (\ref{sec:5}) is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement. Finally, the concluding remarks are given in section (\ref{sec:6}).

%\textbf{Notation}: In order to avoid the risk of any confusion, the notation for the symbols employed in this paper will be defined here.
%\begin{align*}
%\mathbb{R}/ \mathbb{R}^+ &: \ \mbox{the set of all real numbers/positive real numbers.} \\
%\mathbb{Z} &: \ \mbox{the set of non-negative integers.} \\
%\mathcal{R}e\{X \} &: \ \mbox{the real part of a complex variable }X. \\
%\mathcal{I}m\{X \} &: \ \mbox{the imaginary part of a complex variable }X. \\
%a^{\top} &: \ \mbox{the transpose of the vector }a. \\
%z &: \ \parbox[t]{18em}{complex frequency variable used to represent discrete-time systems.} \\
%s &: \ \parbox[t]{18em}{complex frequency variable used to represent continuous-time systems.}
%\end{align*} 
%\section{Notation and Preliminaries}
%Due to the nature of the equations asserted in this paper, it will be convenient express certain equations in a compact manner. A cascade of $q$ frequency response functions $A_1(e^{-j\omega})A_2(e^{-j\omega}) \cdots A_q(e^{-j\omega})$ will be denoted as $[A_1A_2 \cdots A_q](e^{-j\omega})$.

\section{Problem Formulation}
\label{sec:2}
\subsection{Preliminaries}
Let $u[k]$ and $y[k]$ represent the input and output signals of a causal discrete-time system, respectively, where $k$ is a discrete-time instant and $T_s$ is the sampling period. Suppose that these signals are noise-free and have zero initial and final conditions (i.e., $u[k] = y[k] = 0$ for $k \leq 0$ and $k > K_s$). Then, the frequency response function (FRF) of the system can be represented as 
\begin{equation}
G(e^{-j\omega}) = Y(e^{-j\omega}) U^{-1}(e^{-j\omega})
\end{equation}
where
\begin{align}
U(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} u[k]e^{-j \omega T_s k} \label{eq:U_period}\\
Y(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} y[k]e^{-j \omega T_s k}
\end{align} 
are the periodograms of the input and output signals and $\omega \in [-\pi/T_s, \pi/T_s]$. Note that due to the symmetry of the periodograms, it is sufficient to consider $\omega \in [0, \pi/T_s]$ for practical applications. Under these assumptions, it is evident that from a set of sampled time-domain data, one is able to obtain a continuous FRF.  If the data is noisy, then $G(e^{-j\omega})$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}. For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations.

Let the set $\mathscr{P}$ represent the family of all stable, proper, real-rational discrete-time transfer functions with no pole on the unit circle. It is imperative to note that $\mathscr{P}$ is closed under multiplication and addition; in other words, if $P_1(z^{-1}),P_2(z^{-1}) \in \mathscr{P}$, then 
\begin{equation}
\{ P_1(z^{-1})+P_2(z^{-1}),P_1(z^{-1})P_2(z^{-1})\} \in \mathscr{P}
\end{equation}
Suppose that a single-input-single-output (SISO) feedback control system structure is used where the plant is represented as $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ such that $\{N(z^{-1}),M(z^{-1})\} \in \mathscr{P}$. As asserted in \cite{ZD98} and \cite{DFT92}, if $\{N(z^{-1}), M(z^{-1})\} \in \mathscr{P}$, then $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ is called a \textit{coprime factorization} of $G(z^{-1})$ over $\mathscr{P}$.

\subsection{Class of models}
Let the FRF of such a factorized discrete-time SISO plant be defined as follows:
\begin{equation}\label{eq:setpmimo}
G\jo = N\jo M^{-1}\jo, \qquad \forall \omega \in \Omega
\end{equation}
where $\Omega \in [0,\pi/T_s]$. $N\jo$ and $M\jo$ must be FRF's of bounded analytic functions outside the unit circle; for a stable plant, a trivial choice is $N\jo=G\jo$ and $M\jo=1$. A discussion on how to formulate $N\jo$ and $M\jo$ for unstable processes can be found in \cite{KNZ16}. In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
\begin{equation}
\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
\end{equation} 
These FRF's can be determined by considering the frequency response of a parametric model or from a set of input/output data. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case. %In fact, in Section (\ref{sec:4}), a multi-model case will be investigated for the controller synthesis of the power converter control system.

\subsection{Frequency-domain uncertainty} \label{sec:freq_uncertain}
Suppose that the uncertainty associated with a given FRF is described by an additive uncertainty:
\begin{equation}
\begin{aligned} \label{eq:frf_uncertainty}
\hat{N}(e^{-j\omega}) &= N(e^{-j\omega}) + |W_n(e^{-j\omega})| \delta_n e^{j\theta_n} \\
\hat{M}(e^{-j\omega}) &= M(e^{-j\omega}) + |W_m(e^{-j\omega})| \delta_m e^{j\theta_m}
\end{aligned}
\end{equation}
where $|\delta_n| \leq 1$, $|\delta_m| \leq 1$; $\{ \theta_n,\theta_m\} \in [0,2\pi]$; $W_n$ and $W_m$ are the uncertainty weighting filters which can be determined from the covariance of the estimates for a given confidence interval.  As previously stated, $N\jo = G\jo$ and $M\jo = 1$ can be selected for stable systems. Therefore, given the periodogram of $G$, the estimates of the real and the imaginary part of $N\jo$ can be formulated; these estimates are asymptotically uncorrelated and normally distributed with a variance of $\Phi_v(\omega)/2|U\jo|^2$, where $\Phi_v(\omega)$ is the spectrum of the disturbance $v[k]$ at the output of the plant (\cite{Lju99}). The additive uncertainty can be described in the complex plane with a disk centered at $N\jo$ having a radius of $|W_n\jo|$. The uncertainty is characterized by the Rayleigh distribution and can be determined for any probability level. For example, if it is desired to construct an uncertainty disk such that the true frequency response lies within the disk with a probability level of $0.95$, then the radius of this disk will be
\begin{equation} \label{eq:uncertainty_radius}
|W_n\jo| = \sqrt{\frac{5.99 \Phi_v(\omega)}{2|U\jo|^2}}
\end{equation}
The output noise spectrum can be estimated as
\begin{equation} \label{eq:noise_spectrum}
\Phi_v(\omega) = \Phi_y(\omega) - \frac{|\Phi_{uy}(\omega)|^2}{\Phi_u(\omega)}
\end{equation}
where $\Phi_u(\omega)$ is the input spectrum, $\Phi_y(\omega)$ is the output spectrum, and $\Phi_{uy}(\omega)$ is the cross-spectral density of the input and output channels.

\subsection{Class of controllers}
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{rst.eps_tex}}
\caption{$RST$ controller structure}
\label{fig:rst}
\end{figure}
The controller structure that will be considered will be of the $RST$-type. The $RST$ controller is a two-degree of freedom controller which can be used to synthesize the tracking and regulation requirements independently from each other \cite{LZ06}. The general structure of this controller is shown in Fig.~\ref{fig:rst}. Each controller is realized as a polynomial function as follows:
\begin{alignat}{2}
R(z^{-1},\rho) &= r_0 + r_1z^{-1} + \cdots + r_{n_r}z^{-n_r} \label{eq:Rc}\\
S(z^{-1},\rho) &= 1 + s_1z^{-1} + \cdots + s_{n_s}z^{-n_s} \label{eq:Sc}\\
T(z^{-1},\rho) &= t_0 + t_1z^{-1} + \cdots + t_{n_t}z^{-n_t} \label{eq:Tc}
\end{alignat}
where $\{n_s,n_r,n_t\}$ are the orders of the polynomials $R,S$ and $T$, respectively. These controllers can also be represented in a linear regression form as 
\begin{align}
R(z^{-1},\rho)&=\rho_R^\top \phi_{n_r}(z^{-1})= [r_0,r_1,\ldots,r_{n_r}]\phi_{n_r}(z^{-1}); \nonumber \\
S(z^{-1},\rho)&=\rho_S^\top \phi_{n_s}(z^{-1})= [1,s_1,\ldots,s_{n_s}]\phi_{n_s}(z^{-1}); \nonumber \\
T(z^{-1},\rho)&=\rho_T^\top \phi_{n_t}(z^{-1})= [t_0,t_1,\ldots,t_{n_t}]\phi_{n_t}(z^{-1}); \nonumber
\end{align}
where
\begin{align}
\rho^\top &=[\rho_R^\top, \rho_S^\top, \rho_T^\top] \nonumber \\
\phi_x^\top(z^{-1}) &= [1,z^{-1},\ldots,z^{-x}] \nonumber
\end{align}
%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections. 
where $x \in \{n_r,n_s,n_t \}$.

Based on the internal model principle, the controller may contain the disturbance model to achieve a zero steady-state error. Therefore, the polynomials may be pre-multiplied with any arbitrary function that actualizes the desired action. For example, if it is desired to reject a step disturbance at the output, then $S(z^{-1},\rho)$ can be pre-multiplied with $(1-z^{-1})$ (which represents the integral action of the controller). For sinusoidal disturbances at specific frequencies, the polynomials can be pre-multiplied with the function
\begin{equation*}
\theta (z^{-1}) = 1-2z^{-1} \cos(\omega_z T_s) + z^{-2}
\end{equation*}  
where $\omega_z$ is the frequency in $rad/s$ at which the disturbance occurs. %Suppose that there is noise $v$ at a frequency $\omega_z$, and is it desired to attenuate the effects caused by this disturbance (note that (\ref{eq:V}) represents the sensitivity function of interest for this disturbance). Then the $R$ polynomial can be pre-multiplied with $\theta (z^{-1})$ to achieve the desired noise attenuation at the output. In general, any of the $RST$ polynomials can be pre-multiplied with any polynomial that performs the desired action.
%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections.
%For notation purposes, the dependency on the discrete-time frequency variable $z^{-1}$ will be omitted, and the dependency on the controller parameter $\rho$ will remain.

\subsection{Sensitivity Functions}
\label{sec:23}
Since the design techniques introduced in this paper belong to the $\mathcal{H}_{\infty}$ framework, it is  appropriate to consider the various sensitivity functions associated with the $RST$ controller structure. Some sensitivity functions for this process can be asserted as follows:
\begin{align}
\mathcal{S}_1(z^{-1},\rho)&= \frac{y}{d_o} = \frac{M(z^{-1})S(z^{-1},\rho)}{\psi(z^{-1},\rho)}  \label{eq:S0}\\
\mathcal{S}_2(z^{-1},\rho)&= \frac{y}{r} =\frac{N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:T} \\
\mathcal{S}_3(z^{-1},\rho)&= \frac{r-y}{r} =\frac{\psi(z^{-1},\rho)-N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} 
\end{align}
where $\psi(z^{-1},\rho) = N(z^{-1})R(z^{-1},\rho)+M(z^{-1})S(z^{-1},\rho)$, $y$ is the system output, $r$ is the reference input, and $d_o$ is the output disturbance. For notation purposes, the dependency in $z^{-1}$ will be omitted, and will only be reiterated when deemed necessary. Note that all of the sensitivity functions are stable if the zeros of $\psi(\rho)$ lie within the unit circle. The sensitivity functions defined above (and all other sensitivity functions of interest) all contain the same transfer function  $\psi(\rho)$. Therefore, a general construction of the sensitivity function can be expressed as $\mathcal{S}_q(\rho) = \Delta_q(\rho)/ \psi(\rho)$, where $\Delta_q(\rho)$ is a linear function of $R$, $S$ and/or $T$. The subscript $q \in \{ 1,2,\ldots,c\}$ denotes the $q$-th sensitivity of interest and $c$ is the total number of sensitivity functions.

\section{$\mathcal{H}_{\infty}$ Performance via Convex Optimization}
\label{sec:3}
\subsection{General Design Specifications}
\label{sec:general}
In the general $\mathcal{H}_\infty$ control problem, the objective is to find the controller parameters vector $\rho$ such that
\begin{equation} \label{eq:true_hinf}
\sup_{\omega \in \Omega} |H_q(e^{-j\omega},\rho)| < \gamma
\end{equation}
where $\gamma \in \mathbb{R}^+$, $H_q(e^{-j\omega},\rho) = W_q(e^{-j\omega}) \mathcal{S}_q(e^{-j\omega},\rho)$ and $W_q$ is the FRF of a stable weighting filter such that $H_q(e^{-j\omega},\rho)$ has a bounded infinity norm. For notation purposes, the dependency in $e^{-j\omega}$ will be omitted, and will only be reiterated when deemed necessary. The condition in (\ref{eq:true_hinf}) can also be expressed as follows:
\begin{equation} \label{eq:circle}
\gamma^{-1}|W_q \Delta_q(\rho)| < |\psi(\rho)| ; \quad \forall \omega \in \Omega
\end{equation}

It is desired to minimize the upper bound $\gamma$ such that the $\mathcal{H}_{\infty}$ performance condition is satisfied. 
Therefore, the following optimization problem can be considered:
\begin{equation} \label{eq:min1}
\begin{aligned}
& \underset{\rho}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_q\Delta_q(\rho)| < |\psi(\rho)|  \\ 
& & & \forall \omega \in \Omega \quad ; \quad  q \in \mathcal{Q} \subset \{1, 2, \ldots, c\}
\end{aligned}
\end{equation}
Notice that (\ref{eq:min1}) is a non-convex optimization problem.

\begin{figure}
\hspace*{1cm}
\resizebox{0.9\columnwidth}{!}{\input{nxmy2_rad_diff_2.eps_tex}}
\caption{The graphical interpretation of $\mathcal{H}_{\infty}$ constraints in the complex plane}
\label{fig:circle}
\end{figure}

Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\rho)$ and has radius $\gamma^{-1}|W_q\Delta_q(\rho)|$. The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. Fig.~\ref{fig:circle} displays the graphical interpretation of this condition. This geometrical construction will be used to prove the following Lemma:

\begin{lemma}   \label{lem2}
Suppose that $$H_q(\rho,e^{-j\omega})={W_q\jo \Delta_q(\rho,e^{-j\omega})} \psi^{-1}(\rho,e^{-j\omega})$$ is the frequency response of a bounded analytic function outside the unit circle. Then, the following constraint is met
\begin{equation} \label{eq4}
\sup_{\omega \in \Omega}  |H_q(\rho,e^{-j\omega})| < \gamma
\end{equation}
if and only if there exists a finite-impulse-response (FIR) function $F(z^{-1})$ that satisfies
$$
\Re\{\psi(\rho)F(e^{-j\omega})\}>\gamma ^{-1}|W_q\Delta_q(\rho)F(e^{-j\omega})|,  \qquad \forall \omega \in \Omega 
$$
\end{lemma}

{\it Proof :} 
The basic idea is similar to that of  the proof of Theorem~1 in \cite{RM94}. It is clear that (\ref{eq4}) is satisfied if and only if the disk of radius $ \gamma ^{-1}|W_q\Delta_q(\rho)|$ centered at $\psi(\rho)$ does not include the origin for all $\omega \in \Omega$, i.e. $|\psi(\rho)|>\gamma ^{-1}|W_q\Delta_q(\rho)|$. This is equivalent to the existence of a line passing through origin that does not intersect the disk. Therefore, at every given frequency, $\omega$, there exists a complex number $f(e^{-j\omega})$ that can rotate the disk such that it lays inside the right hand side of the imaginary axis. Hence, we have 
\begin{equation}
\label{eq:lem_eq1}
\begin{split}
\Re \left\{ \left[ \psi(\rho) - \gamma ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right] f(e^{-j\omega}) \right\}>0 \\
\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
\end{split}
\end{equation}
where $\Re \{ \cdot \}$ denotes the real part of a complex variable. Since $f(e^{-j\omega}) = |f(e^{-j\omega})|e^{j\theta_f}$, then the above condition can be expressed as
\begin{equation}
\label{eq:lem_eq2}
\begin{split}
\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})|\cos(\theta + \theta_f) \\
\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
\end{split}
\end{equation}
However, (\ref{eq:lem_eq2}) is satisfied if and only if:
\begin{equation}
\label{eq18}
\begin{split}
\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})| \\
\forall \omega \in \Omega
\end{split}
\end{equation}
In \cite{RM94}, it is shown that, $f(e^{-j\omega})$ can be approximated arbitrarily well by the frequency response of a stable transfer function or FIR function $F(z^{-1})$ if and only if 
\begin{equation}
Z=\left( \psi(\rho) - \gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right)^{-1}
\end{equation}
is analytic in the right half plane for all $\gamma_0>\gamma$ and all $\theta \in [0 \, , \, 2 \pi [$. However, $\psi^{-1}(\rho)$ is stable because of the stability of $H_q(\rho)$. On the other hand, by decreasing $\gamma_0$ from infinity to $\gamma$, the poles of $Z$ move continuously with $\gamma_0$. Therefore, $Z$ is not analytic in the right half plane if and only if $Z^{-1}(e^{-j\omega})=0$ for a given frequency, which is not the case because the origin is not in the interior of the circle $\gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta}$.  
{\hfill \ensuremath{\blacksquare}}

The set of all controllers that meet the performance condition defined by the weighted norm of sensitivity functions is asserted in the following theorem.

\begin{theorem}  \label{Th1}
Given the frequency response function $G\jo = N\jo M^{-1}\jo$ and the frequency response of a weighting filter $W_q\jo$, then the following statements are equivalent for a given $q \in \mathcal{Q}$:

{\bf (a)} There exists an $RST$ controller that stabilizes $G$ and

	\begin{equation}
	\label{state_a_single}
	\begin{aligned}
	\sup_{\omega \in \Omega}  | {W_q \mathcal{S}_q(\rho)} | < \gamma 
	\end{aligned}
	\end{equation}

    %\begin{equation}
	%\label{state_a}
	%\sup_{\omega \in \Omega}  | {W_0 (1+GK)^{-1}} | < \gamma
	%\end{equation}

{\bf (b)} There exists an $RST$ controller such that
\begin{equation} \label{state_b_single}
\begin{aligned}
\Re\{\psi(\rho)\}  >\gamma ^{-1}|W_q\Delta_q(\rho)|\quad \forall \omega \in \Omega
 \end{aligned} 
\end{equation}
\end{theorem}
{\it Proof :} ({\bf b} $\Rightarrow$ {\bf a}) 
$\psi(\rho)$ is analytic outside the unit circle and its real part is positive for all $\omega \in \Omega$. Therefore, $\psi(\rho)$ will not encircle the origin when $\omega$ travels along the Nyquist contour, and its inverse is stable. This implies that $R(\rho)$ and $S(\rho)$ stabilizes $G$. On the other hand, we have
\begin{equation}  \nonumber
\begin{aligned}
|\psi(\rho)| \geq \Re\{\psi(\rho)\} \quad 
\forall \omega \in \Omega
\end{aligned}
\end{equation}
which leads to
\begin{equation} \label{eq:the_1_single_2}
\begin{aligned}
|W_q\Delta_q(\rho)| < \gamma |\psi(\rho)| \quad \forall \omega \in \Omega
 \end{aligned}
\end{equation}
Therefore, (\ref{eq:the_1_single_2}) leads to (\ref{state_a_single}) in Statement ({\bf a}).

>>>>

\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}
\bibliographystyle{IEEEtran}

\author{
  Achille Nicoletti and Michele Martino\\ \\
  \textit{\small The European Organization for Nuclear Research (CERN)} \\
  \textit{\small Technology Department, Electrical Power Converters group,} \\
  \textit{\small High Precision Measurements section}
}

\title{Data-driven Controller Design for a Fast-Pulsed Power Converter Control Application}
\date{}

\begin{document}
  \maketitle

  \begin{center}
  \LARGE{\bf{Abstract}}
  \end{center}

The complex structures of today's systems create challenging tasks for the control engineer in designing a viable controller. In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement noise.

Data-driven control methods using frequency-domain data are design schemes that continue to spark the interest of many researchers. The frequency-domain approach offers many advantages compared to time-domain methods :
\begin{itemize}
\item Without knowledge of the transfer function, the dynamics of a system can be captured experimentally through the frequency response.
\item Relative and absolute stability of a closed-loop system can be determined with the knowledge of the open-loop frequency response.
\item Noise disturbance generated in the system can be easily determined using frequency analysis.
\item System uncertainties can be modeled at discrete frequency points (which reduces the conservatism associated with uncertainty modeling). 
\end{itemize}

For this specific application, an $RST$ controller structure was implemented to control the dynamics of the power converter control system. The $RST$ controller structure is an effective discrete-time two-degree of freedom (2DOF) polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}. To design this controller, a $\mathcal{H}_\infty$ loop-shaping method was used to shape a desired sensitivity function. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function \cite{ZD98}. In this method, a convex optimization problem can be formulated if each of the $RST$ polynomials are linearly parameterized \cite{NEK15}.

For this power converter application, it was desired to track a desired reference signal while maintaining sufficient stability margins. Therefore,

\begin{equation}
\int f(t)e^{-st}dt
\end{equation}
\bibliography{linear}
\end{document}
